Binding-Time Analysis for \textsc{miniKanren}

### 2020-05-28 papers/TEASE-LP/example.tex
Minor edit

We assume that all goals are in \emph{canonical normal form}: a goal is a disjunction of conjunctions of either relation calls or unifications; all free variables are brought up into scope by the $\underline{\fresh{}}$ operator on the top level.
Relation calls ($R^k$) and constructors can only have variables ($V$) as their arguments. Unification should have a single variable on the left-hand side and a term ($T$) on the right-hand side, with the exception of unifying two constructors of arity $0$.
We leave out unifications of the zero-arity constructors, since they can either evaluate to a failure or to a success without extending the substitution which can be determined statically.
Any core \miniKanren{} program can be converted to this form.
We use the following representation of the goal in canonical form:
$$Goal = \underline{\fresh{}} \ V_1 \dots V_n \bigvee \bigwedge (\underline{call} \ R^k \ V_1 \dots V_k \mid V \equiv T)$$.

>>>>

We assume that all goals are in \emph{canonical normal form}: a goal is a disjunction of conjunctions of either relation calls or unifications; all free variables are brought up into scope by the $\underline{\fresh{}}$ operator on the top level.
Relation calls ($R^k$) and constructors can only have variables ($V$) as their arguments. Unification should have a single variable on the left-hand side and a term ($T$) on the right-hand side, with the exception of unifying two constructors of arity $0$.
We leave out unifications of the zero-arity constructors, since they can either evaluate to a failure or to a success without extending the substitution which can be determined statically.
Any core \miniKanren{} program can be converted to this form.
We use the following representation of the goal in canonical form:
$$Goal = \underline{\fresh{}} \ V_1 \dots V_n \bigvee \bigwedge (\underline{call} \ R^k \ V_1 \dots V_k \mid V \equiv T)$$
